%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Michael}{Urich}{ \urlstyle{same} \\
\href{mailto:mpu2@pitt.edu}{mpu2@pitt.edu} | 412.303.8722}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{University of Pittsburgh}
\descript{BEng in Electrical Engineering}
\location{Expected Dec 2017 | Pittsburgh, PA}
Conc. in Communications/Signal Processing \\
Swanson School of Engineering \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github: \href{https://github.com/mike-u}{\custombold{mike-u}} \\
LinkedIn:  \href{https://www.linkedin.com/in/mikeurich}{\custombold{mikeurich}} \\
Devpost:  \href{http://devpost.com/MikeUrich}{\custombold{mikeurich}}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}

\subsection{Undergraduate}
Analog Communication Systems \\
Quantitative Systems Neuroscience \\
Analysis and Design of Electronic Circuits \\
Signals and Systems Analysis \\
Music Engineering
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Computing}
Matlab \textbullet{} Python \textbullet{} HTML/JS \\
VHDL\textbullet{} Arduino \textbullet{} Java \\
Git \textbullet{} Linux \textbullet{} \LaTeX 
\sectionsep

\subsection{Design}
SolidWorks \textbullet{} Altera Quartus \\
Autodesk Inventor \textbullet{} GIMP

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%       Hackathons
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Hackathons}

\location{PennApps \textrm{(Sep 2016)}}

\location{Steelhacks \textrm{(Feb 2016)}}

\location{PittApps \textrm{(Jan 2016)}}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Organized for approx 40 students who could not attend PennApps due to weather
\end{tightemize}

\location{MHacks \textrm{(Jan 2015)}}
\sectionsep




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Research}
\runsubsection{Laboratory for Computational Neuroscience} \\
\descript{Undergraduate Research Assistant}
\location{Mar 2016 – Present | Pittsburgh, PA}
Working under supervision of \textbf{\href{http://www.pitt.edu/~zhm4/}{Dr. Zhi-Hong Mao}} to develop a system for detecting eye saccades and blinks through a wearable EEG headset to create an eye-tracking keyboard, which will allow paraplegic patients to communicate without custom modifications to consumer devices. Independently developed support vector machine in Matlab for saccade direction recognition. Publication to be submitted.
\sectionsep

\runsubsection{Pitt Neurobiology Department} \\
\descript{Undergraduate Research Assistant}
\location{Mar 2015 – Sep 2015 | Pittsburgh, PA}
Worked with \textbf{\href{http://hookslab.neurobio.pitt.edu/}{Dr. Bryan Hooks}} with Matlab and ImageJ to develop a novel method of quantifying neuronal connectivity in the motor and sensory cortices of the mouse brain. Publication accepted to BMES 2015 Annual Meeting.
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}

\runsubsection{Design Hub}
\descript{| Webmaster, Club officer}
\location{Jan 2015 – present}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}\item Worked with team of undergraduates to develop \textbf{\href{http://pittdesignhub.com}{Design Hub site}}
\item Part of core group of undergraduates planning workshops and coordinating design teams
\end{tightemize}
\sectionsep

\runsubsection{Dynastim} \\
\location{Jan 2014 – May 2015}
\begin{tightemize}\item Worked with a team of undergraduates and doctors on an
electrophysiology control device for deep brain stimulation
\item Competed in several design and entrepreneurial competitions, progressed to final round of Randall Family Big Idea competition
\item Applied for provisional patent
\end{tightemize}
\sectionsep

\runsubsection{ThereminD} \\
\location{Steelhacks project}
\begin{tightemize}\item Worked with friends to develop \textbf{\href{http://devpost.com/software/theremind}{ThereminD}}, an EEG headband that plays music based on brain signals with theremin-style controls. Used Muse headband integrated wtih Matlab for data acquisition as well as signal processing.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards} 
\begin{tabular}{rll}
2015         & First place at Senior Design Expo, Dynastim project\\
2014	     & First place at Senior Design Expo, Dynastim project\\
2014	     & BK Simon Family Scholar
\end{tabular}
\sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}
